### 2019-01-13 papers/journal/experiments.tex
Results section is completed

%
Table~\ref{tab:satsmt-graph} presents the comparison of the running times of {\smttool} and {\sattool} on VTS variations of sizes 2 to 10.
%
For this comparison we have fixed the total number of molecules minimum twice the node count 
%for $ |N|> 2$ and $2|N| + 1$ for $|N| = 2$
%
%For each variant, we fix 1
and maximum number of parallel
edges to be 2.
%
%
In the table M/O indicates the search results in out of memory, T/O indicates a time out and ``!'' indicate that no model exists for the constraint  (constraints were unsatisfiable).
%In the table we have shown comparison for specific connectivity, for example variant A is checked against any graph with connectivity 2, variant B with connectivity 3 similarly for the rest of the variants.
%
%We have compared our performance with the performance of our earlier CBMC based implementation (old-encoding).
%
As an example, the result of verifying the formula for variation C of 2-connected, 10 compartment graph took 1977.72 secs. with a satisfying result.
%
In comparison, {\sattool} was unable to solve the instance and ran out of memory.
% for $|N|$ greater than 5.
%
% 
The recursive encoding also performed better for the cases where the instance was unsatisfiable (Variant A timing comparison).
%instead of enumeration, not only we got efficiency improved for finding a SAT model but also did better in the case of refutation that no model exist (table~\ref{tab:satsmt-graph} Variant A timing comparison and Variant D with N =2). 
%
Hence with the use of improved encoding of reachability, we were able to scale the system to the biologically relevant compartment size, the
%a much larger compartmentalized system, especially to interesting 
the case of eukaryotic cells with a total number of 10 compartments.
%
Furthermore, we experimented with limits of our tools and found that {\smttool} was able to solve the constraints up to $20$ nodes.

@@

Table~\ref{tab:qbf-graph} presents the result of the QBF tool.
%
The table represents the result of the graph connectivity for each variation of the VTS.  
%
For example, we found that the 3-connected graph satisfies the universal condition for the variation 2. 
%
Note that for this variation existential condition result was the 2-connected graph. 
%
For every other version, the results remained the same.
This implies that for every 3-connected graph, a valid VTS that satisfies all constraints \todo{ elaborate a bit on the constraints} exists.
% 
For biological cells, this means that the whole space of 3-connected graphs is available for evolutionary exploration
%
%The experimentations were done using two QBF solvers: \depqbf and \rarqbf.

>>>>

%
Table~\ref{tab:satsmt-graph} presents the comparison of the running times of {\smttool} and {\sattool} on VTS variations of sizes 2 to 10.
%
For this comparison we have fixed the total number of molecules minimum twice the node count 
%for $ |N|> 2$ and $2|N| + 1$ for $|N| = 2$
%
%For each variant, we fix 1
and maximum number of parallel
edges to be 2.
%
%
In the table M/O indicates the search results in out of memory, T/O indicates a time out and ``!'' indicate that no model exists for the constraint  (constraints were unsatisfiable).
%In the table we have shown comparison for specific connectivity, for example variant A is checked against any graph with connectivity 2, variant B with connectivity 3 similarly for the rest of the variants.
%
%We have compared our performance with the performance of our earlier CBMC based implementation (old-encoding).
%
As an example, the result of verifying the formula for variation C of 2-connected, 10 compartment graph took 1977.72 secs for a satisfying result.
%
In comparison, {\sattool} was unable to solve the instance and ran out of memory.
% for $|N|$ greater than 5.
%
% 
The recursive encoding also performed better for the cases where the instance was unsatisfiable (Variant A timing comparison).
%instead of enumeration, not only we got efficiency improved for finding a SAT model but also did better in the case of refutation that no model exist (table~\ref{tab:satsmt-graph} Variant A timing comparison and Variant D with N =2). 
%
Hence with the use of improved encoding of reachability, we were able to scale the system to the biologically relevant compartment size, the
%a much larger compartmentalized system, especially to interesting 
the case of eukaryotic cells with a total number of 10 compartments.
%
Furthermore, we experimented with limits of our tools and found that {\smttool} was able to solve the constraints up to $18$ nodes.

@@

Table~\ref{tab:qbf-graph} presents the result of the QBF tool.
%
The table represents the result of the graph connectivity for each variation of the VTS.  
%
For example, we found that the 3-connected graph satisfies the universal condition for the variation 2. 
%
Note that for this variation existential condition result was the 2-connected graph. 
%
For every other version, the results remained the same.
%
This implies that for every 3-connected graph there is a valid VTS that satisfies all the constraints of the system.
% 
For biological cells, this means that the whole space of 3-connected graphs is available for evolutionary exploration
%
%The experimentations were done using two QBF solvers: \depqbf and \rarqbf.
